Verifying Cache Coherence Protocols for an infinite family of cache hierarchies

### 2014-02-06 paper/Intuition.tex
this the the correct version

Any two caches $c_1, c_2$ neither of which are an ancestor of the other has a
lowest common ancestor $x$ which is an ancestor of both $c_1$ and $c_2$. $x$
has two distinct children $x_1$ and $x_2$ such that they are the ancestors of
$c_1$ and $c_2$ respectively. For any address $a$, $x_1.\state[a]$ and
$x_2.\state[a]$ are compatible by the second part of
Invariant~\fullref{localCompatibility}. It follows that $x_1.\state[a]$ and
$x_2.\state[a]$ are compatible since these values are smaller than the
respective directory values. From the previous paragraph about the relation
between the states of a cache and its ancestor, it follows that $c_1$ and $c_2$
are also compatible. This proves Invariant \fullref{nonAncestorCompatible}.

@@

Proving the other 3 invariants in Section \ref{second-level} requires using
more properties of the MSI transistions of Figure \ref{trans}, though it is
straightforward.

>>>>

Any two caches $c_1, c_2$ neither of which are an ancestor of the other has a
lowest common ancestor $x$ which is an ancestor of both $c_1$ and $c_2$. $x$
has two distinct children $x_1$ and $x_2$ such that they are the ancestors of
$c_1$ and $c_2$ respectively. For any address $a$, $x_1.\state[a]$ and
$x_2.\state[a]$ are compatible by 
Invariant~\fullref{localCompatibility2}. It follows that $x_1.\state[a]$ and
$x_2.\state[a]$ are compatible since these values are smaller than the
respective directory values. From the previous paragraph about the relation
between the states of a cache and its ancestor, it follows that $c_1$ and $c_2$
are also compatible. This proves Invariant \fullref{nonAncestorCompatible}.

@@

Proving the other 3 invariants in Section \ref{secondLevel} requires using
more properties of the MSI transistions of Figure \ref{trans}, though it is
straightforward.
